\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

\pagestyle{headings}

%\begin{Spacing}{1.4}
I could not have completed this project without the help and support of many who have come along side me in this endeavor. Firstly, thanks to my advisor, Geoffrey Duh, for his guidance, insights, and many hours of dedicated assistance. I would not have even known what I was proposing to do without him making sense of my ramblings. Thank you to my thesis committee members Leopoldo Rodriguez and David Banis, to whom I am grateful for their contributions. Polo, that shovel saved me. Thank you to Martha Works, for her input and direction with my research into understanding my topic from a cultural geography perspective. Thank you Karin Walker and to other staff in the department who helped me navigate the complex bureaucracy of PSU. Thanks to all in my cohort for their support and camaraderie, in particular Tony Hair for his putting up with my incessant, overly-technical geo-babble, and encouraging me to continue even when I wanted to stop.

I must also extend a big thank you to Joe Poracsky and the PSU Geography Department, whose generosity help make this project possible.

Thank you to all those outside of PSU for their encouragement and support through this project: my parents, La Familia Flores, Aaron and Catherine, Tom and Harmony, Josh and Rachel, Matt and Jesse, Renjy and Katy, Dean, Carlos...the list goes on.


To the people of Pellegrini: Gracias a todos. No puedo creer como la gente me ayudaron, especialmente Roberto y Manuel Dantas, David Ruiz, Rafael Dip, y Martín Lasko. Es verdad, sin ustedes yo no haya tenido éxito. Muchas gracias. Espero que yo puede regresar a Nueva Esperanza otra vez. Es una lugar especial a mi, por la gente. Y Playmax, es la gravedad: no me puedo resistir la atracción.

%[Thank you to everyone in Pellegrini. I cannot believe how the people helped me, especially Roberto and Mauel Dantas, David Ruiz, Rafael Dip, y Martín Lasko. It is true, without you all I would not have been successful. Thank you so much. I hope that I can return to Nueva Esperanza again. It is a special place to me, because of the people. And Playmax, it is the gravity: I cannot resist its pull.]

Lastly, but definitely not least, thank you to my wife Aida. You have stood by me through the whole of this process, encouraging and pushing me to continue even when it made life more difficult for you. Te debo. Te quiero, mi bella.
%\end{Spacing}
