\chapter{Notes on the CDL}
\label{appendix:cdl}

Some of the test results and opinions I present throughout this document may lead the reader to question the USDA CDL as source of ground truth data. I believe everyone should approach data critically, and I do not feel badly for the criticism I present of this dataset. My critique is based on my own experience with the data and rumors that have made it to me about the trouble of others with this data. Some have expressed reservations about the published accuracies, and wonder why the USDA has not made the processing workflow public. Despite all this, I have to make three disclaimers about my opinions.

First, I must admit, all my experience has been with the CDL in Kansas. I cannot speak to the accuracy of CDL in other states. I have heard that some other regions are less problematic, though without evidence supporting either view. Perhaps this is the case, and users should have few problems in other areas.

Secondly, I must also acknowledge my sample sites were fairly small, and I only worked closely with the CDL in sample site 1, which might happen to be an anomalous area with a lower-than-average accuracy. Again, other areas may not have the problems I experienced.

Thirdly, I do not have a way to quantify the problems I have observed or to verify the CDL is wrong in the ways I believe it is. Consequentially, all the errors I've found may be within the accuracy range as published, and I should not be as critical of the dataset as I am.

In all, the CDL is a fantastically ambitious dataset, and I do not want to suggest that the USDA has failed. Even if the data have problems, keep in mind that they are classifying the entire continental United States, which has extremely variable conditions and an incredible variety of land covers. That the USDA can achieve any reasonable classification at all is impressive. It is unfortunate that the USDA will not publish the processing methods. Because they won't, it is impossible to know if the rumors I've heard about dubious accuracy assessments are true. As a user, I would appreciate knowing their methods are peer-reviewed, and that the accuracy is actually as good as published.